\PassOptionsToPackage{pdfpagelabels=false}{hyperref}
\documentclass[11pt,a4paper]{moderncv}
\pagenumbering{gobble}
% moderncv themes
\moderncvtheme[green]{classic}                  % optional argument are 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.9]{geometry}
\setlength{\hintscolumnwidth}{3.5cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% Hyperlinks
\usepackage{hyperref}								% to use hyperlinks
\definecolor{linkcolour}{rgb}{0,0.2,0.6}			% hyperlinks setup
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

% personal data
\firstname{Jake}
\familyname{Nielsen}

\title{Mechatronics Engineer}               % optional, remove the line if not wanted
\address{3380 20th St}{San Francisco, CA}    % optional, remove the line if not wanted
%\mobile{+30 698 4385057}                    % optional, remove the line if not wanted
\phone{(408) 816-0751}                      % optional, remove the line if not wanted
%\fax{fax (optional)}                          % optional, remove the line if not wanted
\email{jake.k.nielsen@gmail.com}                      % optional, remove the line if not wanted
%\email{\href{mailto:s.dakourou@gmail.com}{s.dakourou@gmail.com}}                      % optional, remove the line if not wanted
\homepage{github.com/jknielse}%{LinkedIn Profile}}                % optional, remove the line if not wanted
%\extrainfo{additional information (optional)} % optional, remove the line if not wanted
%\photo[64pt][0.4pt]{picture}                         % '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{Some quote (optional)}                 % optional, remove the line if not wanted

% to show numerical labels in the bibliography; only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\vspace{-13mm}

\section{Skills}

\cvline{\textbf{Languages}}{\textbf{Python}, Bash, \textbf{Swift}, \textbf{Objective-C}, C\#, C, C++, JavaScript, Scheme, Assembly}
\cvline{\textbf{Software}}{\textbf{Git}, SVN, Visual Studio, X-Code, Vim, Windows, Linux, Mac}

\section{Work Experience}
\cventry{Aug 2014 - Present}{Software Tools Engineer (Python, Swift)}{\newline{}Apple Inc}{Cupertino}{}
{Development and maintenance of Safari and WebKit's CI systems (driven by Buildbot).
    \newline{}Developed tool for locally testing the CI system (previously tested in-production).
\newline{}Developed tool for machine provisioning to save developer time spent manually reimaging mac minis}

\cventry{May 2013 - Aug 2013}{Firmware Engineer Intern (C\#, C++)}{\newline{}Virtium Inc}{Rancho Santa Margarita}{}
{Development of IPC library capable of up to 7GB/s throughput.
    \newline{}Further development of continuous integration unit testing for SSD firmware.
\newline{}Received an \textbf{outstanding} on work evaluation.}

\cventry{Sept 2012 - Feb 2013}{Mobile Software Engineering Intern (Objective-C, Node.js, Mongoose)}{\newline{}Rebellion Media Inc}{Waterloo}{}
{Development of iOS apps from mock-ups.
\newline{}App backend development.
\newline{}Received an \textbf{outstanding} on work evaluation.}

\cventry{Jan 2012 - Apr 2012}{Cofounder and Software Developer (Objective-C)}{\newline{}Crouton Labs Inc}{Waterloo}{}
{Developing iOS applications to allow restaurant customers to order and pay for food.
\newline{} Ruthless attention to look-and-feel.
\newline{}Received an \textbf{outstanding} on work evaluation.}

\cventry{May 2011 - Aug 2011}{Manufacturing Software Engineering Intern (TCL)}{\newline{}Sandvine Inc}{Waterloo}{}{}

\cventry{May 2010 - Aug 2010 \newline{}\newline{}Sept 2010 - Dec 2010}{Software and Hardware Developer Intern (C++, VB.Net)}{\newline{}University of Waterloo}{}{}
{Developing hardware and firmware for an experimental configurable 3D pressure-sensing surface.
    \newline{}Developing firmware, and software for an experimental 3-axis CNC lathe, and a 3D scanner.
\newline{}Received an \textbf{outstanding} on work evaluation.}

\section{Projects and Competitions}

\cvline{\textbf{Autonomous Boat}}
{Designed the hardware, sofware, and PID control system for a boat capable of autonomously navigating a water-course.}

\cvline{\textbf{Computing Collective} (Co-founder)}
{Worked on start-up that commercializes the grid computing space, winners of the \$25,000 Velocity Venture Fund competition.
\newline{}Involved in the software development of said platform in python.}

\cvline{\textbf{VeloCity Entrepreneurial Incubator}}
{Returning resident at VeloCity, which helps students who are working on start-ups, by providing funding, mentorship and a collaborative environment.}

\section{Education}
%\cventry{year--year}{Degree}{Institution}{City}{\textit{Grade}}{Description}
\cventry{2009 - 2014}{Mechatronics Engineering}{\newline{}University of Waterloo}{}{}{
Relevant Courses: RTOS, Sensors and Instrumentation, SISO Control Systems, MIMO Control Systems, Autonomous Mobile Robotics, Mechatronic System Integration}

\end{document}
